Calculating Entropies With Nested Sampling

### 2017-02-02 paper/ms.tex
updated numbers - challenging

% These were produced with a random number seed of 0
% on commit 25301bb
% With 10 particles, 1000 mcmc steps per NS iteration, and 1000 reps.

\begin{align}
H_{\x}     &= 7.345  \pm 0.027 \\  % max depth was 30
H_{\d}     &= 703.96 \pm 0.31  \\  % max depth was 1000
H_{\x, \d} &= 712.27 \pm 0.31      % max depth was 1000
\end{align}

@@

Converting these to differential entropies, we obtain
\begin{align}
H'_{\x}     &= 1.131  \pm 0.027 \\  % max depth was 30
H'_{\d}     &= 697.75 \pm 0.31  \\  % max depth was 1000
H'_{\x, \d} &= 699.84 \pm 0.31      % max depth was 1000
\end{align}
and therefore a mutual information of {\query a negative value! Oh dear!
Something is wrong. Update: well I found a bug after this, so it might
change. :)}

>>>>

% These were produced with a random number seed of 0
% on commit 947317948d04255ea0baff7a7d3e357b0c2f7fcb
% With 10 particles, 1000 mcmc steps per NS iteration.

\begin{align}                    % (num_particles, mcmc_steps, max_depth, reps)
H_{\x}    &= 7.328 \pm 0.025 \\% (100, 1000, 30.0,  122)
H_{\d}    &= 960.4 \pm 3.7   \\% (100, 1000, 1200.0, 99)
H_{\x,\d} &= 968.6 \pm 3.4   \\% (100, 1000, 1200.0, 99)
\end{align}

@@

To convert these to differential entropies, we need to add the appropriate
log-volume to each. These are $-6.215$, $-782.02$, and
$-788.23$ respectively.
\begin{align}
H'_{\x}     &= 1.113 \pm 0.025 \\
H'_{\d}     &= 178.4 \pm 3.7   \\
H'_{\x, \d} &= 180.4 \pm 3.4
\end{align}
and therefore a mutual information of {\query a negative value! Oh dear!
Something is wrong. Update: well I found a bug after this, so it might
change. :)}
